On the presentation of orthogonal groups over polynomial rings

### 2019-05-27 dl-paper.tex
Some fixes

 Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
 \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
 Since the subgroup $C = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
 (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C$,
 which implies the assertion. \qedhere \end{proof}

@@

Now for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)],\]
hence $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right] \subseteq \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]), \St(\Phi, M)\right]$ and therefore \[K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \St(\Phi, M)\right].\]

It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
Thus, to verify the assertion it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.
Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, but in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}. \end{proof}

@@

\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
Notice that a priori $K(\alpha, \beta)$ depends on a choice of $\delta$, however as the next proposition shows, there is no such dependence.

\begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$. Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$. \end{prop}
\begin{proof} Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$. Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$. By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.

@@

The following proposition is directly inspired by~\cite[Proposition~4.3]{Tu83}.
\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_1$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
\end{prop}
\begin{proof}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}

Let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$. Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf. the first part of the proof of~\cref{lem:orbit-action}). Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta}$ and $c = 1 - \epsilon abm'$.
Applying~\cref{SR:obtuse} to a pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
 = T_\beta(b) T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right) , u (1 - am) \right) \sim \\ \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h \cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc), u (1 - am) \right) = \\ = \left([x_\beta(b), x_\alpha(aX^{-1})] g, h', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline} 
 where the last equivalence is obtained as follows:
 \begin{multline} \nonumber
 h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\ = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim \\ \sim h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
\end{multline}

Let us prove $\text{R3}_{1,1}$ in the special case when $\alpha$ and $\beta$ form a sharp angle. As before, we can assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$. Set $\epsilon = N_{\alpha,-\beta}$.
Applying~\cref{SR:sharp} we obtain that
\begin{multline} \label{eq:sharp-formula1}
 T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
 \begin{multline} \label{eq:sharp-formula2}
 h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
The expressions in the right-hand sides of~\eqref{eq:sharp-formula1}--\eqref{eq:sharp-formula2} are clearly symmetric under transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies $\text{R3}_{1,1}$.
\end{proof}

>>>>

 Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
 \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
 Since the subgroup $C_0 = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
 (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
 which implies the assertion. \qedhere \end{proof}

@@

Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$.
It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
Since $C_0$ is generated by the above commutators and $\overline{\St}(\Phi, A[X], XM[X])$ is a normal subgroup of $\St(\Phi, A[X])$
we obtain that $C_0 \subseteq \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1$ and consequently that
$K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1.$

It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $C_1$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
Thus, it remains to show that commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.
Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, 
 and in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}. \end{proof}

@@

\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}

\begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$. 
Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$. 
In particular, $K(\alpha, \beta)$ does not depend on a choice of the root $\delta$. \end{prop}
\begin{proof} Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$. Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$. By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.

@@

The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_1$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
\end{prop}
\begin{proof}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}

Let us verify $\text{R2}_1$. 
Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf. the first part of the proof of~\cref{lem:orbit-action}).
Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
Applying~\cref{SR:obtuse} to a pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
 = T_\beta(b) T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right), u (1 - am) \right) \sim \\
 \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h', u (1 - am) \right) = \\
 = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g, h'', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot$ 
  and the last congruence is obtained as follows:
 \begin{multline} \nonumber
 h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
 = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
 h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
\end{multline}

Let us prove $\text{R3}_{1,1}$ in the special case when $\alpha$ and $\beta$ form a sharp angle.
As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$.
Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
\begin{multline} \label{eq:sharp-formula1}
 T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline}

\begin{multline} \label{eq:sharp-formula2}
 h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
Relation $\text{R3}_{1,1}$ now follows from the fact that expressions in the right-hand sides of~\eqref{eq:sharp-formula1}--\eqref{eq:sharp-formula2} are symmetric under
 the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$.
\end{proof}
